Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-03-21 article.tex
semantic line-break in discussion

In this article, we introduced a suite of Python packages we developed
for defining and simulating dynamical systems and reaction networks.
These packages are deeply integrated with
\acp{IDE}, enabling code analysis tools to identify errors
prior to execution and assist in refactoring and code completion. We
adopted standard modern Python syntax to ensure seamless IDE
integration, supported by the extensive Python community.

Our approach differs from previous tools in that both the model
definition and its compilation into an
\ac{ODE} function are entirely Python-based. This approach simplifies the
development of various simulation methods, including performance
enhancements that exploit specific model structures. Importantly, being
Python-based does not compromise performance compared to C/C++ tools, as
the \ac{ODE} functions can be \ac{JIT} compiled using Numba.

>>>>

In this article,
we introduced a suite of Python packages we developed
for defining and simulating dynamical systems and \acp{CRN}.
These packages are deeply integrated with \acp{IDE},
enabling code analysis tools to identify errors prior to execution
and assist in refactoring and code completion.
We adopted standard modern Python syntax to ensure seamless IDE integration,
supported by the extensive Python community.

Our approach differs from previous tools in that both the model
definition and its compilation into an \ac{ODE} function are entirely Python-based.
This approach simplifies the development of various simulation methods,
including performance enhancements that exploit specific model structures.
Importantly, being Python-based does not compromise performance compared to C/C++ tools,
as the \ac{RHS} functions can be \ac{JIT} compiled using Numba.
